Example penalized LTRC survival model with simulated data

### 2021-06-23 example.Rmd
Typo fixes for example

## Survival probabilities and calibration
### Survival probabilities
Models fit with `glmnet` now have `survfit` method which can be used to generate survival curves. Note that the values of `x` and `y` used to train the model must also be passed so that the baseline hazard can be computed.

@@

Plots using base `R` graphics can quickly be generating using the `plot.survfit()` method, which produces a survival curve for each patient in the test set.

>>>>

## Survival probabilities and calibration
### Survival probabilities
Models fit with `glmnet` now have a `survfit` method which can be used to generate survival curves. Note that the values of `x` and `y` used to train the model must also be passed so that the baseline hazard can be computed.

@@

Plots using base `R` graphics can quickly be generated using the `plot.survfit()` method, which produces a survival curve for each patient in the test set.
